\bf Comparing the Power of Plot Designs to Reveal Correlation

### 2015-12-16 paper/paper.Rnw
Updates

\begin{itemize}
  \item Factor 1: Plot design, levels = scatter plot, overlaid time series
  \item Factor 2: Sample size, levels = 12, 24, 48, 96
  \item Factor 3: True plot correlation, levels 
\end{itemize}

@@

# Need to keep only evaluations done by subject who completed at least 10
x <- data.frame(table(full$subj_id))
keep <- x$Var1[x$Freq>9]
full.sub <- filter(full, subj_id %in% keep)
full.sub$r <- round(full.sub$correlation, 1)
full.sub$rsgn <- ifelse(full.sub$r >= 0, 1, 0)
full.sub$rabs <- abs(full.sub$r)
#full.sub$rabs <- factor(full.sub$rabs)
full.sub$plot <- ifelse(full.sub$test_param == 0, "S", "L")
full.sub <- select(full.sub, subj_id, correct, r, rsgn, rabs, smoothed, n, plot, log_time, response_0, actual_location)#[,c(1,7, 15,16,17,20:26)]
full.sub$attempts <- sapply(strsplit(as.character(full.sub$response_0), ","), length)
full.sub$weights = 1/(full.sub$attempts) #weights are actually number of attempts in the glm
full.sub <- full.sub %>% transform(response_0= strsplit(as.character(response_0), ",")) %>% unnest(response_0)
full.sub$correct <- ifelse(full.sub$response_0 == full.sub$actual_location, 1, 0) #fixing correct for multiple guesses
#full.sub$rpos <- ifelse(full.sub$r > 0, full.sub$r, 0)
#full.sub$rneg <- ifelse(full.sub$r < 0, full.sub$r, 0)
full.sub$alpha <- log(.05/0.95)
#full.sub$correct.prop <- full.sub$correct/full.sub$attempts #correct.prop - proportion of correct selections, weights - number of attempts
#weirw.csv(full.sub, "stata.csv") #exporting data to other programs
m8l <- glmer(correct.prop~offset(alpha) + rabs*rsgn + smoothed + n + (1|subj_id), data=filter(full.sub, plot == "L"), family="binomial", weights=attempts)
m8s <- glmer(correct.prop~offset(alpha) + rabs*rsgn + smoothed + n + (1|subj_id), data=filter(full.sub, plot == "S"), family="binomial", weights=attempts)
#pander(summary(m8l), justify=c('left', 'right', 'right', 'right', 'right', caption="Model fit for overlaid lines"))
#pander(summary(m8s)$coefficients, justify=c('left', 'right', 'right', 'right', 'right'), caption="Model fit for scatter plots")
#library(xtable)
line.fit <- summary(m8l)$coefficients
scatter.fit <- summary(m8s)$coefficients
colnames(scatter.fit)[4] <- "p-value"
rownames(scatter.fit) <- c("Intercept", "abs(r)", "sign(r)", "smooth", "sample size", "Interaction(r+, r-)")
#colnames(line.fit)[4] <- "p-value"
#rownames(line.fit) <- c("Intercept", "abs(r)", "sign(r)", "smooth", "sample size", "Interaction(r+, r-)")
kable(scatter.fit, format="latex", digits=2, caption="Scatter plot")
kable(line.fit, format="latex", digits=2, caption="Overlaid Lines")
@
\end{table}

@@

\begin{table}
\label{tab2}
\centering
\caption{Mixed Linear Model fit for time taken to make a selection}
<<timefit, dependson='powerfit', echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
timelmer <-  lmer(log_time ~ smoothed + r + n + rsgn*r + plot + plot*smoothed 
                  + plot*r + plot*n + plot*rsgn*r + plot*correct + (1|subj_id), data=full.sub)
time.fit <- summary(timelmer)$coefficients
pv <- function(x){
  p <- 2*(1-pt(x, 1835))
}
p.value <- sapply(time.fit[,3], pv)
time.fit <- cbind(time.fit, p.value)
time.fit <- time.fit[c(1, 2, 4, 3, 5, 8, 7, 6, 9, 11, 10, 12, 14, 13),] #separate into main effects then interaction effects in same order
kable(time.fit[1:7,], format="latex", caption="Main Effects")
kable(time.fit[8:14,], format="latex", caption="Interaction Effects")
@
\end{table}

>>>>

\begin{itemize}
  \item Factor 1: Plot design, levels = scatter plot, overlaid time series
  \item Factor 2: Sample size (t), levels = 12, 24, 48, 96
  \item Factor 3: True plot correlation, levels 
\end{itemize}

@@

# Need to keep only evaluations done by subject who completed at least 10
x <- data.frame(table(full$subj_id))
keep <- x$Var1[x$Freq>9]
full.sub <- filter(full, subj_id %in% keep)
full.sub$r <- round(full.sub$correlation, 1)
full.sub$rsgn <- ifelse(full.sub$r >= 0, 1, 0)
full.sub$rabs <- abs(full.sub$r)
#full.sub$rabs <- factor(full.sub$rabs)
full.sub$plot <- ifelse(full.sub$test_param == 0, "S", "L")
full.sub <- select(full.sub, subj_id, correct, r, rsgn, rabs, smoothed, n, plot, log_time, response_0, actual_location)#[,c(1,7, 15,16,17,20:26)]
full.sub$attempts <- sapply(strsplit(as.character(full.sub$response_0), ","), length)
full.sub$weights = 1/(full.sub$attempts) #weights are actually number of attempts in the glm
full.sub <- full.sub %>% transform(response_0= strsplit(as.character(response_0), ",")) %>% unnest(response_0)
full.sub$correct <- ifelse(full.sub$response_0 == full.sub$actual_location, 1, 0) #fixing correct for multiple guesses
#full.sub$rpos <- ifelse(full.sub$r > 0, full.sub$r, 0)
#full.sub$rneg <- ifelse(full.sub$r < 0, full.sub$r, 0)
full.sub$alpha <- log(.05/0.95)
#full.sub$correct.prop <- full.sub$correct/full.sub$attempts #correct.prop - proportion of correct selections, weights - number of attempts
#weirw.csv(full.sub, "stata.csv") #exporting data to other programs
m8l <- glmer(correct.prop~offset(alpha) + rabs*rsgn + smoothed + n + (1|subj_id), data=filter(full.sub, plot == "L"), family="binomial", weights=attempts)
m8s <- glmer(correct.prop~offset(alpha) + rabs*rsgn + smoothed + n + (1|subj_id), data=filter(full.sub, plot == "S"), family="binomial", weights=attempts)
#pander(summary(m8l), justify=c('left', 'right', 'right', 'right', 'right', caption="Model fit for overlaid lines"))
#pander(summary(m8s)$coefficients, justify=c('left', 'right', 'right', 'right', 'right'), caption="Model fit for scatter plots")
#library(xtable)
line.fit <- summary(m8l)$coefficients
scatter.fit <- summary(m8s)$coefficients
colnames(scatter.fit)[4] <- "p-value"
rownames(scatter.fit) <- c("Intercept", "abs(r)", "sign(r)", "smoothed", "t", "Interaction(r+, r-)")
#colnames(line.fit)[4] <- "p-value"
#rownames(line.fit) <- c("Intercept", "abs(r)", "sign(r)", "smooth", "sample size", "Interaction(r+, r-)")
kable(scatter.fit, format="latex", digits=2, caption="Scatter plot")
kable(line.fit, format="latex", digits=2, caption="Overlaid Lines")
@
\end{table}

@@

\begin{table}
\label{tab2}
\centering
\caption{Mixed Linear Model fit for time taken to make a selection}
<<timefit, dependson='powerfit', echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
timelmer <-  lmer(log_time ~ smoothed + r + n + rsgn*r + plot + plot*smoothed 
                  + plot*r + plot*n + plot*rsgn*r + plot*correct + (1|subj_id), data=full.sub)
time.fit <- summary(timelmer)$coefficients
pv <- function(x){
  p <- 2*(1-pt(x, 1835))
}
p.value <- sapply(time.fit[,3], pv)
time.fit <- cbind(time.fit, p.value)
time.fit <- time.fit[c(1, 2, 4, 3, 5, 8, 7, 6, 9, 11, 10, 12, 14, 13),] #separate into main effects then interaction effects in same order
rownames(time.fit) <- c("Intercept", "Smoothed", "t", "r", "sign(r)", "r*sign(r)", "correct", "Plot", "Plot*Smoothed", "Plot*t", "Plot*r", "Plot*sign(r)", "Plot*r*sign(r)", "Plot*correct")
kable(time.fit[1:7,], format="latex", caption="Main Effects (Overlaid Lines)")
kable(time.fit[8:14,], format="latex", caption="Interaction Effects (Scatter plot)")
@
\end{table}
